---
title: "Multiple regression app"
author: "Gregory Verleysen"
date: "16-2-2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Reading the file
This app performs multiple regression on any csv file you want.

First you select a csv file on your PC.
Just like in R you can specify header (are the names of variables included)
and what the separator and quote marks are.

```{r,echo=TRUE}
data<-read.csv("cars.csv",header=TRUE,sep=",",quote="")
```

## Data exploration
Next you can inspect the data with structure and summary.
Structure will give information about the types of variables.
Summary will show some descriptive statistics for each variable.

```{r,echo=TRUE}
summary(data)
```

## Multiple regression and correlation
Finally you can choose an outcome variable and multiple variables that you want as predictors.
Linear regression will show the regression output for this model.
Correlation will show the correlations between the variables that you selected.


## Multiple regression example
```{r,echo=TRUE}
summary(lm(X.mpg.~X.disp.+X.hp.+X.drat.,data))
```

